MultiDataGrowthAssessPico

### 2023-12-08 Code/MultiDataGrowthAssessPico.Rmd
Removed redundant lines

#remove redundant objects
remove(OD720_unnest,
       deltaOD_unnest,
       UnnestedLogData,
       OD720truncLog_unnest,
       deltaODtruncLog_unnest,
       UnnestedTruncLogData,
       UnnestedFullData
       )

>>>>

#remove redundant objects
remove(OD720_unnest,
       deltaOD_unnest,
       UnnestedLogData,
       OD720truncLog_unnest,
       deltaODtruncLog_unnest,
       UnnestedTruncLogData
       )
